Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-16 latex/comp_or.tex
Paper Compo OR update.

\cite{MesquitaSanches2023} proposed a method that attends these objectives: a pallet building and arrangement plan with a routing option that maximizes the benefit-cost ratio for the smooth execution of pickup and delivery transport missions. They develop a heuristic that can be executed on a simple handheld computer (like a laptop or a tablet) and that provides a solution quickly enough to keep this cargo handling time under an hour. This work seeks to improve their results in terms of quality and performance by the use of computer parallelism and by minimizing the distance between the next node destined pallets and the cargo door.

@@

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it  }&{\it  }&  \specialcell{{\bf 1.00}\\-} \\%11495

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &    21.31  &  17.35    &   24.24   &   27.39    &  29.31     &  27.06     &     \\%  11012
		&                                                & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.0 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &    24.33  &   17.26   &   24.70   &  24.81     &   27.71    &  24.93        &    \\% 9966
		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.7}\\% 151

@@

The upper bound is the objective function value of a linear programming relaxation of the problem, demonstrating that no integer viable solution can have an objective value greater than this.

@@

{\it Shims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was .... times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the execution {\it race condition} management limited {\it mpShims} performance.

@@

@@

There was some expectation on this post-improvement method as it could have minimized the distances of travel of the pallets to the ramp door, but unfortunately, after running all scenarios and problem instances, there was no improvement in minimizing these distances.

@@

@@

We converted \cite{MesquitaSanches2023} {\it Shims} into a process-based parallel computing heuristic, which we called {\it Multiprocessing Shims} or {\it mpShims}, that quickly finds good solutions for a wide range of problem sizes, an essential addition as it surpassed all {\it Shims} results, our first contribution.

We also carryed out 126 experiments with each method on synthetic data based on real data from the {\it Brazilian Air Force} transportation history.

Another important contribution is that we employed the {\it iRace} package \citep{LopezIbanezManuel2016} to fine tune the {\it mpShims} parameters, guaranteeing the best possible performance for the instances under training and testing.

>>>>

\cite{MesquitaSanches2023} proposed a method that attends these objectives: a pallet building and arrangement plan with a routing option that maximizes the benefit-cost ratio for the smooth execution of pickup and delivery transport missions. They develop a heuristic that can be executed on a simple handheld computer (like a laptop or a tablet) and that provides a solution quickly enough to keep this cargo handling time under an hour.

In this work, we raise three hypotheses for improvements to the work of \cite{MesquitaSanches2023}:
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) The distances to move pallets on unloading in the next node could be minimized to benefit unloading costs.

So, this work seeks to improve their results in terms of quality and performance by using computer parallelism, CG balancing between {\it Shims}' phases, and minimizing the distance between the next node-destined pallets and the cargo door.

@@

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60 }&  \specialcell{{\bf 1.00}\\-} \\%15266

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &    21.31  &  17.35    &   24.24   &   27.39    &  29.31     &  27.06     &   0.96  \\%  14666
		&                                                & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.0 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &    24.33  &   17.26   &   24.70   &  24.81     &   27.71    &  24.93        &  0.94  \\% 14374
		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.7}\\% 151

@@

The upper bound is the objective function value of a linear programming relaxation of the problem, demonstrating that no integer viable solution can have an objective value greater (in maximization) than this.

@@

{\it Shims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was 2 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing, for reading and writing, the CG deviation and the list of items among the processes (pallets), the {\it race condition} management limited {\it mpShims} performance.

@@

So, to confirm or not Hypothesis (3), that the distances to move pallets on unloading in the next node could be minimized to benefit unloading costs. We modeled this improvement as follows.

@@

There was some expectation on this post-improvement method as it could have minimized the distances of travel of the pallets through the ramp door, but unfortunately, after running all scenarios and problem instances, there was no improvement in minimizing these distances.

@@

\subsection{Discussion summary}

In this work, we raised three hypotheses for improvements to the work of \cite{MesquitaSanches2023}:

(1) Computer parallelism could improve {\it Shims}'s performance: {\it mpShims} was twice as faster as {\it Shims}. This hypothesis was confirmed.

(2) The {\it Shims}' results may have been inferior in that of \cite{MesquitaSanches2023}; it could be that a sequential approach to pallet building may have lead to a premature stop due to the torque constraints. This hypothesis was confirmed as the results were improved by 5\% on average with the inclusion of a CG balancing integer programming procedure.

(3) The distances to move pallets on unloading in the next node could be minimized to benefit unloading costs. This hypothesis was not confirmed. We implemented an integer programming procedure to minimize these distances, but the results proved that any change in {\it Shims} or {\it mpShims} outcomes could turn the solutions unfeasible due to the CG balance constraints.

A new question is raised about whether it is worth using parallelism as, although {\it mpShims} was twice as fast as {\it Shims}, the results of {\it Shims} were still better than those of {\it mpShims}. May this question be solved through the real-world application of these methods.

@@

We converted \cite{MesquitaSanches2023} {\it Shims} into a process-based parallel computing heuristic, which we called {\it Multiprocessing Shims} or {\it mpShims}, that quickly finds good solutions for a wide range of problem sizes, our first contribution.

We also carried out 126 experiments with each method on synthetic data based on real data from the {\it Brazilian Air Force} transportation history.

Other important contributions are that we checked three hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; but the integer programming procedure to minimize pallets' travel in the cargo bay did not improve the results.

And another important contribution is that we employed the {\it iRace} package \citep{LopezIbanezManuel2016} to fine tune the {\it mpShims} volume threshold parameter, guaranteeing the best possible performance for the instances under training and testing.
